### 2013-02-15 doc/icml2013/algo.tex

\section{A Method of Moments Algorithm}
\label{sec:algo}

In this section, we will outline an algorithm to recover the parameters
$\pi$ and $B$ of the mixture of linear regressions model.

% Motivate how we can recover $B$ from regression by lower order moments
Our goal is to recover the parameters $(\pi, B)$, ideally from lower
order moments. Conventionally, when using the method of moments, the
moments of observed variables are expressed algebraically in terms of
the model parameters. Using these equations, we attempt to solve for the
model parameters using empirical estimates of the moments.

Let us consider the response variable $y$, 
\begin{align}
  y &=& \innerp{\beta_h}{x} + \epsilon,
\end{align}
where $\epsilon \sim \normal{0}{\sigma^2}$ is the observation noise.  It
is natural to consider regression on the data $\{\xni,
\yni\}_{i=1}^{N}$, but it would only help us find the mean regression
coefficients, $M_1 = \E[\beta_h] = \sum_h \pi_h \beta_h$, which are insufficient to
identify the model. Let us consider some more low powers of $y$, noting
that taking the expectation gives us the corresponding low-order
moments,
\begin{align}
  y^2 &= \innerp{\beta_h\tp{2}}{x\tp{2}} + \epsilon \innerp{\beta_h\tp{2}}{x\tp{2}} + \epsilon^2 \label{eq:y2} \\ 
  y^3 &= \innerp{\beta_h\tp{3}}{x\tp{3}} + 3 \epsilon \innerp{\beta_h\tp{2}}{x\tp{2}} \notag \\
  &+ 3 \epsilon^2 \innerp{\beta_h}{x} + \epsilon^3. \label{eq:y3} 
\end{align}
Regression with the second order moments would give us $M_2 = \E[\beta_h
\tp{2}] = \sum_h \pi_h \beta_h\tp{2}$ which can identify $\pi$ and the
subspace spanned the $\beta_h$, but not the $\beta_h$ themselves. To see
this, note that the eigen-decomposition of $M_2$ is not unique.
\todo{explain better}.

This brings us to regression with the third order moments, giving us the
tensor $M_3 = \E[\beta_h \tp{3}] = \sum_h \pi_h \beta_h\tp{3}$.
\citet{AnandkumarGeHsu} show that these three moments suffice to
identify $\pi$ and $B$ and provide an efficient algorithm to recover the
parameters.

We note that the eigendecomposition of $M_2$ is not sufficient to
recover the $\beta_k$ because they are not necessarily orthogonal to
each other. \citet{AnandkumarGeHsu2012} describes an approach that uses
rotates $M_3$ to an orthogonal basis by using the whitening transform of
$M_2$. The eigenvectors and eigenvalues recovered from the
eigendecomposition of $M_3(W, W, W)$ can be de-whitened to recover the
$\beta_k$ and $\pi_k$.

% Describe the rest of the algorithm.
This description completes a sketch of the algorithm, described in
\algorithmref{algo:spectral-experts}. Going ahead, we have yet to show
that the regression is well-behaved which we will do in
\sectionref{sec:regression}. This is of concern because the regression
problem we have has variance introduced from component selection,
independent of any observation noise. We will show that we can indeed
efficiently recover $M_2$ and $M_3$ using ideas from low-rank
regression. Finally, we will outline the tensor power method to recover
$B$ and $\pi$ given these two quantities, $M_2$ and $M_3$ in
\sectionref{sec:tensor-power}.

\begin{theorem}
  Recovery analysis of mixture of linear regressions.
\end{theorem}
\begin{proof}
\end{proof}

\begin{algorithm}[t]
  \caption{Spectral Experts}
  \label{algo:spectral-experts}
  \begin{algorithmic}[1]
    \REQUIRE $\mathcal{D} = \{ (\xn{1}, \yn{1}), \cdots, (\xn{N}, \yn{N}) \}$
    \REQUIRE $K$, the number of clusters, $\sigma^2$ 
    \STATE Recover $M_1$ using least-squares regression on $\mathcal{D}$.
    \STATE Recover $M_2, M_3$ using low-rank regression on $\mathcal{D}$.
    \STATE Return the eigenvectors $\beta_k$ and eigenvalues $\pi_k$ of $M_3$ using $M_2$.
  \end{algorithmic}
\end{algorithm}

We will conclude this section by
discussing some identifiability concerns for our algorithm.

@@

% In the case of the mixture of linear regressions, we have two observed
% quantities, $x$ and $y$. Unfortunately, because $y$ is a scalar
% quantity, we have only one equation for every moment of $y$, and with
% this naive approach, would have to consider $O( (K+1) D)$ moments to
% recover $B \in \Re{K \times D}$ and $\pi \in \Re^K$.

% To keep the discussion simple, we will consider the case where there is
% no noise, i.e.  $\sigma^2 = 0$. In this case, the moments of $y$ are,
% \begin{eqnarray*}
%   \E[ y ] &=& (\sum_{k=1}^{K} \pi_{k} \beta_k)^T x \\
%           &=& M_1^T \E[x] \\
%   \E[ y^2 ] &=& \sum_{k=1}^{K} \pi_{k} \E[(\beta_k^T x)]^2 \\
%   &=& \sum_{k=1}^{K} \pi_{k} (\beta_k\tp{2} \odot \E[x\tp{2}]) \\
%   &=& M_2 \odot \E[x\tp{2}] \\
%   \E[ y^p ] &=& M_p \odot \E[x\tp{p}].
% \end{eqnarray*}
% 
% We note that joint moments with $x$ will not help either; consider
% \begin{eqnarray}
%   \E[ y^p x^q ] &=& M_p \odot E[ x\tp{p+q} ].
% \end{eqnarray}
% The elements of $\E[ y^p x^q ]$ are linear combinations of $\E[y^p]$,
% and hence we do not get any new equations; \todo{This isn't exactly
% correct; should we even be presenting this line of reasoning?}. This is
% to be expected, since any information about the $\beta$s is really
% encoded in $y$, and not in the $X$.

>>>>

\section{Spectral Experts Algorithm}
\label{sec:algo}

In this section, we describe our Spectral Experts algorithm
for estimating model parameters $\theta = (\pi, B, \sigma^2)$.
Our algorithm consists of two steps:
(i) low-rank regression to estimate certain symmetric tensors;
and (ii) tensor factorzation to recover the parameters.
% Motivate how we can recover $B$ from regression by lower order moments
%ideally from lower order moments.
%Conventionally, when using the method of moments, the
%moments of observed variables are expressed algebraically in terms of
%the model parameters. Using these equations, we attempt to solve for the
%model parameters using empirical estimates of the moments.

%%% first moment
To warm up, let us consider linear regression
on the response $y$ given $x$.
From the model definition, we have $y = \beta_h^\top x + \epsilon$ where
$\epsilon \sim \normal{0}{\sigma^2}$, and $h$ is a random quantity
independent of $x$.
We can average over this randomness by defining
the average regression coefficients
$M_1 \eqdef \sum_{h=1}^k \pi_h \beta_h$.
Now we can express $y$ as a linear function of $x$ with coefficients $M_1$
plus some noise $\eta_1(x)$:
\begin{align}
  y &= \innerp{M_1}{x} +
  \underbrace{(\innerp{M_1 - \beta_h}{x} + \epsilon)}_{\eqdef \eta_1(x)}.
\end{align}
The noise $\eta_1(x)$ is the sum of two terms:
(i) the \emph{mixing noise} $\innerp{M_1 - \beta_h}{x}$
due to the random choice of the mixture component $h$,
and (ii) the \emph{observation noise} $\epsilon \sim \normal{0}{\sigma^2}$.
Although the noise depends on $x$,
it still has zero mean conditioned on $x$.
We will later show that we can
perform linear regression on the data $\{\xni,
\yni\}_{i=1}^{n}$ to produce a consistent estimate of $M_1$
under identifiability conditions.
But clearly, knowing $M_1$ is insufficient
for identifying all the parameters $\theta$.

%%% second moments
Intuitively, performing regression on only $y$ given $x$ provides only first-order
information.  The key insight is that we can perform regression
on higher order powers to obtain more information about the parameters.
Specifically, for an integer $p \ge 1$, let us define the average
$m$-th order tensor power of the parameters as follows:
\begin{align}
M_p &\eqdef \sum_{h=1}^k \pi_h \beta_h\tp{p}. \label{eqn:Mp} % \in (\Re^{d})\tp{p}.
\end{align}
Now consider performing regression on $y^2$ given $x\tp{2}$.
Expanding $y^2 = (\innerp{\beta_h}{x} + \epsilon)^2$,
using the fact that $\innerp{\beta_h}{x}^p = \innerp{\beta_h\tp{p}}{x\tp{p}}$,
we have:
\begin{align}
y^2 &= \innerp{M_2}{x\tp{2}} + \sigma^2 + \eta_2(x), \label{eqn:y2} \\
\eta_2(x) &= \innerp{\beta_h\tp{2} - M_2}{x\tp{2}} + \epsilon \innerp{\beta_h\tp{2}}{x\tp{2}} + (\epsilon^2 - \sigma^2). \nonumber
%y^2 &= \innerp{M_2}{x\tp{2}} + \sigma^2 + \underbrace{\innerp{\beta_h\tp{2} - M_2}{x\tp{2}} + \epsilon \innerp{\beta_h\tp{2}}{x\tp{2}}}_{\eqdef \eta_2(x)} + (\epsilon^2 - \sigma^2) \label{eq:y2}, \\
\end{align}
Again, we have expressed $y^2$ has a linear function of $[x\tp{2}, 1]$
with regression coefficients $[M_2, \sigma^2]$, plus noise.
Importantly, the noise has mean zero; 
in fact each of the three terms has mean zero
by (i) definition of $M_2$, (ii) independence of $\epsilon$ and $h$,
and (iii) the fact that $\E[\epsilon^2] = \sigma^2$.

Performing regression yields a consistent estimate of $[M_2, \sigma^2]$,
but does not identify all the parameters $\theta$.
In particular, $B$ is only identified up to rotation:
if $B = [\beta_1 \mid \cdots \mid \beta_k]$ satisfies
$B \diag(\pi) B^\top = M_2$, then $(B Q) \diag(\pi) (Q B^\top)$
for any orthogonal matrix $Q$.
%Regression with the second order moments would give us $M_2 = \E[\beta_h
%\tp{2}] = \sum_h \pi_h \beta_h\tp{2}$ which can identify $\pi$ and the
%subspace spanned the $\beta_h$, but not the $\beta_h$ themselves. To see
%this, note that the eigen-decomposition of $M_2$ is not unique.
%\todo{explain better}.

%%% third moment
Let us now proceed to the third moment with the hope that it will
provide additional information.
We can write $y^3$ as a linear function of $x\tp{3}$ plus zero mean noise:
\begin{align}
y^3 &= \innerp{M_3}{x\tp{3}} + 3\sigma^2 \innerp{M_1}{x} + \eta_3(x), \label{eqn:y3} \\
\eta_3(x) &= \innerp{\beta_h\tp{3} - M_3}{x\tp{3}}
+ 3 \epsilon \innerp{\beta_h\tp{2}}{x\tp{2}} \nonumber \\
&+ 3(\epsilon^2 \innerp{\beta_h}{x} - \sigma^2 \innerp{M_1}{x})
+ \epsilon^3, \nonumber
\end{align}
where $\E[\eta_3(x) \mid x] = 0$.
Performing regression on our data yields estimates $M_3$ and $\sigma^2 M_1$.
It turns out that knowledge of $M_2$ and $M_3$ are sufficient to recover
all the parameters.

%We note that the eigendecomposition of $M_2$ is not sufficient to
%recover the $\beta_k$ because they are not necessarily orthogonal to
%each other.

% Full algorithm
Now we are ready to state our full algorithm, which we call Spectral Experts.
The full algorithm is described in \algorithmref{sec:algo}.
First, we perform two regressions according to \refeqn{y2}
and \refeqn{y3} to recover the compound parameters $M_2$ and $M_3$.
The first regression \refeqn{estimateM2}
produces estimates of $\hat M_2$ and $\hat\sigma^2$;
the second regression \refeqn{estimateM3} produces $\hat M_3$ (we ignore $\hat S_1$).
Since $M_2$ and $M_3$ have low rank structure,
we use nuclear norm regularization \cite{Tomioka2011,NegahbanWainwright2009}
to exploit this structure.
The regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(2)}$
are set to $O(\frac{1}{\sqrt{n}})$.
See \sectionref{sec:regression} for more details.

Second, given a matrix $M_2$ and tensor $M_3$ of the form in \refeqn{Mp},
\citet{AnandkumarGeHsu2012} showed that due to symmetry of $M_2$ and $M_3$,
we can efficiently perform tensor factorization of the whitened
version of $M_3$.  The eigenvalues and eigenvectors
directly yield the parameters $\pi$ and
$\{\beta_h\}$.
See \sectionref{sec:tensor-power} for details.
%\citet{AnandkumarGeHsu2012} showed that given $M_2$ and $M_3$
%of the form in \refeqn{Mp},
%the robust tensor power method can be employed to recover $\pi$ and
%$\{\beta_h\}$.

%\citet{AnandkumarGeHsu2012} describes an approach that uses
%rotates $M_3$ to an orthogonal basis by using the whitening transform of
%$M_2$. The eigenvectors and eigenvalues recovered from the
%eigendecomposition of $M_3(W, W, W)$ can be de-whitened to recover the
%$\beta_k$ and $\pi_k$.

% Describe the rest of the algorithm.
%This description completes a sketch of the algorithm, described in
%\algorithmref{algo:spectral-experts}. Going ahead, we have yet to show
%that the regression is well-behaved which we will do in
%\sectionref{sec:regression}. This is of concern because the regression
%problem we have has variance introduced from component selection,
%independent of any observation noise. We will show that we can indeed
%efficiently recover $M_2$ and $M_3$ using ideas from low-rank
%regression. Finally, we will outline the tensor power method to recover
%$B$ and $\pi$ given these two quantities, $M_2$ and $M_3$ in
%\sectionref{sec:tensor-power}.

\begin{algorithm}[t]
  \caption{Spectral Experts}
  \label{algo:spectral-experts}
  \begin{algorithmic}[1]
    \INPUT Data $\mathcal{D} = \{ (\xn{1}, \yn{1}), \cdots, (\xn{n}, \yn{n}) \}$.
    \OUTPUT Parameters $\hat\theta = (\hat \pi, [\hat \beta_1 \mid \cdots \mid \hat \beta_k], \hat\sigma^2)$.
    \STATE Estimate compound parameters $M_2, M_3$ using \textbf{low-rank regression}:
    \begin{align}
      &[\hat M_2, \hat \sigma^2] = \arg\min_{M_2,\sigma^2} \label{eqn:estimateM2} \\
      &\quad\frac{1}{2n} \sum_{(x,y) \in \sD} (\innerp{M_2}{x\tp{2}} + \sigma^2 - y^2)^2 + \lambda_n^{(2)} \|M_2\|_*, \nonumber \\
       &[\hat M_3, \hat S_1] = \arg\min_{M_3,S_1} \label{eqn:estimateM3} \\
       &\quad\frac{1}{2n} \sum_{(x,y) \in \sD} (\innerp{M_3}{x\tp{3}} + \innerp{S_1}{x} - y^3)^2 + \lambda_n^{(3)} \|M_3\|_*. \nonumber
    \end{align}
    \STATE Estimate the coefficients $\{\beta_h\}$ using \textbf{tensor factorzation}:
    \begin{enumerate}
      \item [(a)] Compute whitening matrix $W \in \Re^{d \times k}$ (such that $W^\top
      \hat M_2 W = I$) using SVD.
      \item [(b)] Compute the eigenvalues $\{\lambda_h\}_{h=1}^k$
      and eigenvectors $\{v_h\}_{h=1}^k$
      of the whitened tensor $M_3(W, W, W) \in \Re^{k \times k \times k}$
      by using the robust tensor power method.
    \item [(c)] Set parameter estimates $\hat\pi_h = \frac{1}{\lambda_h^2}$
    and $\hat\beta_h = (W^{\top})^\dagger (\lambda_h v_h)$.
    \end{enumerate}
  \end{algorithmic}
\end{algorithm}

Our main theoretical result shows that Spectral Experts returns
consistent parameter estimates (see Appendix
\begin{theorem}[Convergence of Spectral Experts]
Let $\sD$ consist of $n$ i.i.d. points drawn from the mixture
of linear regressions model with parameter $\theta^*$.
Assume that $\E[[1,\unfold(x\tp{2})]\tp{2}] \succ 0$ 
and $\E[[x,\unfold(x\tp{3})]\tp{2}] \succ 0$.
Then the parameter estimates $\hat\theta$ returned by
\algorithmref{algo:spectral-experts}, with the columns appropriate permuted,
satisfies $\sigma^2 \le \epsilon$,
$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
and for all $h \in [k]$,
$\|\hat\beta_h - \beta^*_h\| \le \epsilon$,
for some error tolerance $\epsilon = O(\frac{kd^2}{n (\min_h \pi_h^*)})$.
\end{theorem}
\begin{proof}
Let $T^* = M_3^*(W^*, W^*, W^*)$.
By Theorem 5.1 of \cite{AnandkumarGeHsu2012},
\end{proof}

% Method of moments interpretation
%Though we have motivated Spectral Experts using regression on powers
%of $y$ given powers of $x$,
%we can also think of the algorithm in terms of
%the method of moments.  Specifically,
%the optimality conditions for the regression of $M_2$ and $M_3$ are:
%\begin{align}
%\E[x\tp{2} (\innerp{M_2}{x\tp{2}} + \sigma^2 - y^2)] = 0, \\
%\E[x\tp{3} (\innerp{M_3}{x\tp{3}} + 3 \sigma^2 \innerp{M_1}{x} - y^3)] = 0.
%\end{align}

@@

% In the case of the mixture of linear regressions, we have two observed
% quantities, $x$ and $y$. Unfortunately, because $y$ is a scalar
% quantity, we have only one equation for every moment of $y$, and with
% this naive approach, would have to consider $O( (k+1) D)$ moments to
% recover $B \in \Re{k \times D}$ and $\pi \in \Re^k$.

% To keep the discussion simple, we will consider the case where there is
% no noise, i.e.  $\sigma^2 = 0$. In this case, the moments of $y$ are,
% \begin{eqnarray*}
%   \E[ y ] &=& (\sum_{k=1}^{k} \pi_{k} \beta_k)^T x \\
%           &=& M_1^T \E[x] \\
%   \E[ y^2 ] &=& \sum_{k=1}^{k} \pi_{k} \E[(\beta_k^T x)]^2 \\
%   &=& \sum_{k=1}^{k} \pi_{k} (\beta_k\tp{2} \odot \E[x\tp{2}]) \\
%   &=& M_2 \odot \E[x\tp{2}] \\
%   \E[ y^p ] &=& M_p \odot \E[x\tp{p}].
% \end{eqnarray*}
% 
% We note that joint moments with $x$ will not help either; consider
% \begin{eqnarray}
%   \E[ y^p x^q ] &=& M_p \odot E[ x\tp{p+q} ].
% \end{eqnarray}
% The elements of $\E[ y^p x^q ]$ are linear combinations of $\E[y^p]$,
% and hence we do not get any new equations; \todo{This isn't exactly
% correct; should we even be presenting this line of reasoning?}. This is
% to be expected, since any information about the $\beta$s is really
% encoded in $y$, and not in the $X$.

### 2013-02-15 doc/icml2013/regression.tex

In the previous section, we described an algorithm for the mixture of
linear regressions using regression to recover $M_2$ and $M_3$,
described by \equationref{eq:y2} and \equationref{eq:y3}, as
a subroutine. In this section, we will characterize the rate of
convergence of regression.

Analysis for regression in the fixed and random design settings have
been studied before\citep{HsuKakadeZhang}, however our setup differs
substantially from the noise models assumed in the literature. In our
scenario, the variance in the estimation comes not only from the
Gaussian observation noise (which has been studied before), but also
from the variance in the latent variable $h$.

@@

In general, the optimization problem we'd like to solve is,
\begin{align}
  \hat M_p &= 
  \arg\min_{M_p}& \frac{1}{2N} \| \vec y - \opX(M_p) \|_2^2 + \frac{\lambda_N}{K} \sum_{h=1}^K \| (M_p)_{(h)} \|_* \label{eq:regression}.
\end{align}

@@

\begin{lemma}(Restricted Strong Convexity)
  Let $\opX$ be the linear operator previously defined. Then,
  $$\kappa{\opX} \ge Y$$.
\end{lemma}
\begin{proof}
  \todo{Do I need to transform rewrite $M_p$ in terms of orthogonal components?}

@@

\begin{lemma}(Bounded Error)
  Let $\opX$ be the linear operator previously defined. Then,
  $$\opX^*(\epsilon) \le Y$$.
\end{lemma}
\begin{proof}
  \begin{align*}
    \frac{\opX^*(\epsilon)}{N} 
    &= \frac{1}{N}\sum_{i=1}^{N} \epsilon_i \innerp{x_i\tp{p}}{M_p} \\
    &= \frac{1}{N}\sum_{i=1}^{N} (\innerp{x_i\tp{p}}{M_p - \beta_i\tp{p}} + \varepsilon)  \innerp{x_i\tp{p}}{M_p}.
  \end{align*}
  Let $M_p - \beta_i\tp{p} = \tilde M_i$ and consider it to be a random
  variable.
  \begin{align*}
    \frac{\opX^*(\epsilon)}{N} 
    &= \frac{1}{N}\sum_{i=1}^{N} \innerp{\tilde M_i}{x_i\tp{2p}} + \varepsilon \innerp{M_p}{x_i\tp{p}} \\
    &\le \frac{1}{N}\sum_{i=1}^{N} \|\tilde M_i\|_{op} \|x_i\|^{2p} + \varepsilon \|M_p\|_{op}\|x_i\|^{p} \\
    &\le \|M_p\|_{op} ( \frac{1}{N}\sum_{i=1}^{N} \|x_i\|^{2p} + \varepsilon \|x_i\|^{p} ).
  \end{align*}

>>>>

In this section, we analyze step 1 of the Spectral Experts
algorithm: that of recovering the compound parameters $M_2,M_3$
from data.

%In the previous section, we described an algorithm for the mixture of
%linear regressions using regression to recover $M_2$ and $M_3$,
%described by \equationref{eqn:y2} and \equationref{eq:y3}, as
%a subroutine. In this section, we will characterize the rate of
%convergence of regression.

\cite{candesPhaseLift} regresses on the square of the response,
because that's the observation.

Analysis for regression in the fixed and random design settings have
been studied before \citep{HsuKakadeZhang}, however our setup differs
substantially from the noise models assumed in the literature. In our
scenario, the variance in the estimation comes not only from the
Gaussian observation noise (which has been studied before), but also
from the variance in the latent variable $h$.

@@

In general, the optimization problem we'd like to solve is,
\begin{align}
  \hat M_p &= 
  \arg\min_{M_p}& \frac{1}{2N} \| \vec y - \opX(M_p) \|_2^2 + \frac{\lambda_n}{K} \sum_{h=1}^K \| (M_p)_{(h)} \|_* \label{eq:regression}.
\end{align}

@@

\begin{lemma}[restricted strong convexity]
Let $\opX$ be the linear operator previously defined. Then,
$$\kappa(\opX) \ge Y$$.
\end{lemma}
\begin{proof}
  \todo{Do I need to transform rewrite $M_p$ in terms of orthogonal components?}

@@

\begin{lemma}[bounded error]
  Let $\opX$ be the linear operator previously defined. Then,
  $$\opX^*(\epsilon) \le Y$$.
\end{lemma}
\begin{proof}
  \begin{align*}
    \frac{\opX^*(\epsilon)}{N} 
    &= \frac{1}{N}\sum_{i=1}^{N} \epsilon_i \innerp{x_i\tp{p}}{M_p} \\
    &= \frac{1}{N}\sum_{i=1}^{N} (\innerp{x_i\tp{p}}{M_p - \beta_i\tp{p}} + \varepsilon)  \innerp{x_i\tp{p}}{M_p}.
  \end{align*}
  Let $M_p - \beta_i\tp{p} = \tilde M_i$ and consider it to be a random
  variable.
  \begin{align*}
    \frac{\opX^*(\epsilon)}{N} 
    &= \frac{1}{N}\sum_{i=1}^{N} \innerp{\tilde M_i}{x_i\tp{2p}} + \varepsilon \innerp{M_p}{x_i\tp{p}} \\
    &\le \frac{1}{N}\sum_{i=1}^{N} \|\tilde M_i\|_{op} \|x_i\|^{2p} + \varepsilon \|M_p\|_{op}\|x_i\|^{p} \\
    &\le \|M_p\|_{op} ( \frac{1}{N}\sum_{i=1}^{N} \|x_i\|^{2p} + \varepsilon \|x_i\|^{p} ).
  \end{align*}
